```{r}
library(wordVectors)
library(magrittr)
library(word2vec)
library(ggplot2)
library(directlabels)
library(readr)
```
# LOAD ALL MATRICES #
```{r}
decade <- c(#"pre_1899",
                  "1900_1909",
                  "1910_1919",
                  "1920_1929",
                  "1930_1939",
                  "1940_1949",
                   "1950_1959",
                   "1960_1969",
                   "1970_1979",
                   "1980_1989",
                   "1990_1999",
                   "2000_2009"
                 )

dir= 'C:\\Users\\isak\\Documents\\'
#dir = '/home/sveisa/'
for (dec in decade) {
  model_name = paste(dir,'matrix',dec, '.csv', sep="")
  assign(paste0("matrix", c(dec)),
  read.csv(paste(dir,"matrix", dec, ".csv", sep=""), row.names = 1, header= TRUE))
}
```

# ANALYZE ALL #
```{r}
for (dec in decade) {
wordlist_df <- read.csv(paste(dir,"wordlist.csv", sep=""))
words = c(wordlist_df[["WORD1"]])
results<-data.frame(get(paste0("matrix", c(dec)))[words,])
results$time<-dec
results <- cbind(rownames(results),data.frame(results, row.names=NULL))
colnames(results)[1] <- "words" 
assign(paste0("results", c(dec)), results)
#write.csv(results, file=paste("results", decade, '.csv', sep=""), row.names = FALSE)
}
```

# MERGE RESULTS #
```{r}
df<-do.call("rbind", list(
   results1900_1909,
   results1910_1919,
   results1920_1929,
  # results1930_1939,
   results1940_1949#,
  # results1950_1959,
  # results1960_1969,
  # results1970_1979,
  # results1980_1989,
  # results1990_1999,
  # results2000_2009
  ))
```

# LOAD ONE MATRIX #
```{r}
decade = "1920_1929"
matrix <- read_csv(paste("/home/sveisa/matrix",decade,".csv", sep=""))
matrix <- as.data.frame(matrix)
colnames(matrix)[1] <- "words"
samp2 <- matrix[,-1]
rownames(samp2) <- matrix[,1]
df<-samp2
```
### IN ONE MATRIX - SEARCH FOR WORDS AND CREATE VISUALIZATION###
```{r}
wordlist_filename = "/home/sveisa/wordlist.csv" #words=c("mad","elegant")
wordlist_df <- read.csv(wordlist_filename)
words = c(wordlist_df[["WORD1"]])
df<-data.frame(df[words,])
df$time<-decade
df <- cbind(rownames(df), data.frame(df, row.names=NULL)) #if you need to make rownames a column
colnames(df)[1] <- "words" 
assign(paste0("results", c(decade)), as.data.frame(df))
#write.csv(get(paste0("results", c(decade))),file=paste("results",decade,'.csv', sep=""),row.names = FALSE)
```

# VIZ 1 #
```{r}
df$wordtime<-paste(df$words,df$time)
Visualization<-ggplot(data=df,aes(x=gender_proj,y=aff_proj,label=wordtime)) + geom_text()
Visualization+ theme_bw() +ylim(-.25,.25) +xlim(-.25,.25)
```

# VIZ 2 #
```{r}
df_long<-reshape2::melt(data=df, id.vars = c("words", "time"),variable.name = "Topic",value.name = "count")
df_long$gender_words<-paste(df_long$Topic,df_long$words)
df_long<-df_long[grepl("gender", df_long$Topic),] #select dimension (or remove rows containing string, if grepl is prefaced by !)
p <- ggplot(data=df_long, aes(x=time, y=as.numeric(count), group=words, colour=words)) +  geom_line(aes(linetype=words), size=0.5) + geom_point(aes(shape=words)) + geom_dl(aes(label=words,color=words), method = list("last.points", hjust=0.9))
p + ggtitle("") + xlab("Time") + ylab("Ratio") + theme_bw() +ylim(-.25,.25)+ theme(legend.position="none")
p
#ggsave("chart.png", width = 10, height = 6,limitsize=FALSE)
